LSOA domestic Electricty and Gas maps

### 2021-08-26 LSOA Deprevation.Rmd
Adding the layover maps and histograms for the analysis of the results

merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, 
                    by = "LSOA11CD", # you have to use the LSOA11CD variable you just created! 'lsoa11cd' doesn't exist in these two datasets...
                    all = TRUE)
names(merged_imd)
merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
summary(merged_imd)
```
```{r Mapping the change in IMD Score}
merged_imd$lsoa11cd <- merged_imd$LSOA11CD #creating a variable with the LSOA code in the same name as in sf_data - check what you created above!
lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
names(lsoa_imd20152019)## fixed
ggplot2::ggplot(lsoa_imd20152019) +
 geom_sf(aes(fill=imd_diff))+ 
 scale_fill_continuous(name="Change in IMD score", low="green",high="red")+
 labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA IMD}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = imd_diff)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA IMD}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, 
                    by = "LSOA11CD", # you have to use the LSOA11CD variable you just created! 'lsoa11cd' doesn't exist in these two datasets...
                    all = TRUE)
names(merged_imd)
merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
summary(merged_imd)
```
```{r Mapping the change in IMD Score}
merged_imd$lsoa11cd <- merged_imd$LSOA11CD #creating a variable with the LSOA code in the same name as in sf_data - check what you created above!
lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
names(lsoa_imd20152019)## fixed
ggplot2::ggplot(lsoa_imd20152019) +
 geom_sf(aes(fill=imd_diff))+ 
 scale_fill_continuous(name="Change in IMD score", low="green",high="red")+
 labs(caption ="Solent (all LSOAs)")

#Histogram
lsoa_imd20152019$pc_diff <-100* (lsoa_imd20152019$imd_diff/lsoa_imd20152019$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
#####Looking at the cities in more detail
```{r Southampton LSOA IMD}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = imd_diff)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA IMD}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```

### 2021-08-26 LSOA Fuel poverty.Rmd
Adding the layover maps and histograms for the analysis of the results

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Winchester LOSA Fuel Pov 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Southampton LSOA Fuel Pov 2012 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

>>>>

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Winchester LOSA Fuel Pov 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")
# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$fp2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$fp2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$fp_diff <-  as.numeric(merged_df$fp2018) - merged_df$fp2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=fp_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")

#Histogram 
lsoa_fuelpov20122018$pc_diff <-100* (lsoa_fuelpov20122018$fp_diff/lsoa_fuelpov20122018$fp2012)
t_diff <-dplyr::select(as.data.frame(lsoa_fuelpov20122018),LSOA11CD, 'LSOA Code', fp2012, fp2018, fp_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
##### Looking at cities in more detail
```{r Southampton LSOA Fuel Pov 2012 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

### 2021-08-26 LSOA domestic Elec and Gas.Rmd
Adding the layover maps and histograms for the analysis of the results

```{r Mapping the electricty consumption of the LSOAs}
lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
ggplot2::ggplot(lsoa_merged_sf) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all LSOAs)")
#Mapping it
```

##### Looking at cities in more detail        
```{r Southampton LSOA dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

@@

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```

@@

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```

#####Cities in more detail
```{r Southampton change in LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Southampton")

>>>>

```{r Mapping the electricty consumption of the LSOAs}
lsoa_merged_sf <- merge(lsoa_sf_data, lsoa_elecData) #merging the boundaries and energy data
ggplot2::ggplot(lsoa_merged_sf) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all LSOAs)")
#Mapping it
```
####Map with Overlay
```{r Check leaflet for dom electricity consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_merged_sf)
st_coord_sys$epsg

#Trasforming the coord systen
if(st_coord_sys$epsg !=4326){
map_df_trans <- st_transform(lsoa_merged_sf, "+proj=longlat +datum=WGS84")
}
```
```{r Plotting leaflet dom electricity consumption map}
qpal <- colorNumeric("Reds", map_df_trans$`Mean domestic electricity consumption \n(kWh per meter)`, n=9)

leaflet(map_df_trans) %>%
addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(`Mean domestic electricity consumption \n(kWh per meter)`),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```
##### Looking at cities in more detail        
```{r Southampton LSOA dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

@@

lsoa_sf_de20102019$pc_diff <- 100*(lsoa_sf_de20102019$de_diff/lsoa_sf_de20102019$de2010)
t_diff <-  dplyr::select(as.data.frame(lsoa_sf_de20102019), 
                         LSOA11CD, `Lower Layer Super Output Area (LSOA) Name.y`,
                         de2010, de2019, de_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x = pc_diff)) +
  geom_histogram()
```
####Map with Overlay 
```{r Check leaflet for Change in dom elec consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_sf_de20102019)
st_coord_sys$epsg

#Transforming the coord system
if(st_coord_sys$epsg !=4326) {
  map_df_trans <- st_transform(lsoa_sf_de20102019, "+proj=longlat +datum=WGS84")
}

```
```{r Plotting leaflet for change in dom elec consumption map}
qpal <- colorNumeric("Reds", map_df_trans$de_diff, n=9)

leaflet(map_df_trans) %>% 
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(de_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD ),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

@@

###Map with Overlay
```{r Check leaflet for dom gas consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_merged_sf_gas)
st_coord_sys$epsg

#Transforming the coord system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(lsoa_merged_sf_gas, "+proj=longlat +datum=WGS84")
}
```
```{r Plotting leaflet dom gas consumption}
qpal <- colorNumeric("Reds", map_df_trans$`Mean consumption (kWh per meter)`, n=9)

leaflet(map_df_trans) %>%
  addTiles() %>%
  addPolygons(color= ~qpal(`Mean consumption (kWh per meter)`), 
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),

              highlight=highlightOptions(
                weight=5,
                color="#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Lower Layer Super Output Area (LSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(lsoa_dgas20102019) + geom_sf(aes(fill=dg_diff))+ 
                  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_dgas20102019)
st_coord_sys$epsg

#Transforming the coor system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(lsoa_dgas20102019, "+proj=longlat +datum=WGS84")
}

```
```{r Plotting leaflet for change in dom gas consumption map}
qpal <- colorNumeric("Reds", map_df_trans$dg_diff, n=9)

leaflet(map_df_trans) %>%
  addTiles() %>%
  addPolygons(color = ~qpal(dg_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```
#####Cities in more detail
```{r Southampton change in LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_dgas20102019, LAD11NM == "Southampton")
